Variation in use of East Asian Late Paleolithic weapons: A study of tip cross-sectional area of stemmed points from Korea

### 2022-10-19 analysis/paper/paper.qmd
put code for null ##

```{r}
# ADD CODE TO REPLACE NULL WITH ACTUAL VALUES
n_sites <- NULL # replace this with the number
min_n_points <- NULL # replace this with the number
n_radiocarbon_ages <- NULL # replace this with the number
n_sites_with_radiocarbon_ages <- NULL # replace this with the number

@@

We used `r n_radiocarbon_ages` radiocarbon ages to explore the temporal pattern of the function of stemmed points. We excluded assemblages that have no radiocarbon dates. We arranged `r n_sites_with_radiocarbon_ages` assemblages dated from 45ka to 14.8ka to explore variation in TCSA over time.

@@

We computed artefact TCSA values for `r n_sites` sites that contain more than `r min_n_points` stemmed points to observe variation between sites (@fig-tcsa-sites) Sites with fewer than `r min_n_points` stemmed points were grouped under the category of 'other'. Among the sites in our sample, Suyanggae has the most stemmed points and the widest range of TCSA values. This suggests that people made stemmed points for a variety of different purposes in Suyanggae. The TCSA values for Nosanri and Sibuk are have a narrower range of lower values, which indicates less diverse functions for stemmed points. Wolpyeng and Yongsujaeul have similar amounts of stemmed points to Nosanri and Sibuk, but exhibit wider distributions of TCSA values. Yongsandong has the second most stemmed points and TCSA shows a similar distribution to Yongsakul.

@@

# radiocarbon data per assemblage
sitedate <- read_excel(here("analysis/data/raw_data/TCSA_site_info.xlsx"))

@@

korean_archaeological_site_locations_tcsa <- 
  tcsa_site_ass %>% # maybe some sites are missing TSCA values in this table?
  mutate(Site_name = str_remove(Assemblage, "_.*")) %>%  
  full_join(korean_archaeological_site_locations) %>% 
  drop_na(min_tcsa)

>>>>

# get rid of 'Other'
tcsa_site_num <- tcsa_site %>% 
  filter(site_name_top != 'Other')

###########
# radiocarbon data per assemblage
sitedate <- read_excel(here("analysis/data/raw_data/TCSA_site_info.xlsx"))

########
mydata_ages_na <- mydata_ages %>%
  drop_na(age)

# count radiocarbon ages

n_sites <- length(unique(tcsa$Site_name))
min_n_points <- nrow(tcsa_site) # should I get rid of "Other" in the figure?, if then, it's nrow(tcsa_site_num)
# n_radiocarbon_ages <- NULL # we only have one age per assemblage
n_sites_with_radiocarbon_ages <- nrow(mydata_ages_na)
```

@@

We used radiocarbon ages to explore the temporal pattern of the function of stemmed points. We excluded assemblages that have no radiocarbon dates. We arranged `r n_sites_with_radiocarbon_ages` assemblages dated from 45ka to 14.8ka to explore variation in TCSA over time.

@@

We computed artefact TCSA values for `r n_sites` sites that contain more than `r min_n_points` stemmed points to observe variation between sites (@fig-tcsa-sites) Sites with fewer than 4 stemmed points were grouped under the category of 'other'. Among the sites in our sample, Suyanggae has the most stemmed points and the widest range of TCSA values. This suggests that people made stemmed points for a variety of different purposes in Suyanggae. The TCSA values for Nosanri and Sibuk are have a narrower range of lower values, which indicates less diverse functions for stemmed points. Wolpyeng and Yongsujaeul have similar amounts of stemmed points to Nosanri and Sibuk, but exhibit wider distributions of TCSA values. Yongsandong has the second most stemmed points and TCSA shows a similar distribution to Yongsakul.

@@

@@

# korean_archaeological_site_locations_tcsa <- 
#   tcsa_site_ass %>% 
#   mutate(Site_name = str_remove(Assemblage, "_.*")) %>%  
#   full_join(korean_archaeological_site_locations) %>% 
#   drop_na(min_tcsa)

korean_archaeological_site_locations_tcsa <- tcsa %>% 
  full_join(korean_archaeological_site_locations) %>% 
  drop_na(min_tcsa)
